---
title: "Week4 Project Part2"
author: "Melody Zhang"
date: '2022-06-27'
output: pdf_document
---

## Part2: Basic Inferential Data Analysis Instructions

### 1. Load the ToothGrowth data and perform some basic exploratory data analyses.
```{r load data}
data("ToothGrowth")
library(ggplot2)
```

### 2.Provide a basic summary of the data.
```{r summary}
summary(ToothGrowth)
dim(ToothGrowth)
head(ToothGrowth)
str(ToothGrowth)
ToothGrowth$dose <- as.factor(ToothGrowth$dose)
```

### 3.Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. (Only use the techniques from class, even if there's other approaches worth considering)

Firstly, analyse the relationship between tooth length and supplementary methods.
```{r supp}
ggplot(ToothGrowth, aes(x=dose,y=len)) +     
  geom_boxplot(aes(fill=dose)) +
  facet_grid(~ supp)
```

Secondly, analyze the relationship between tooth length and drug dose.
```{r dose}
ggplot(ToothGrowth, aes(x=supp,y=len)) +     
  geom_boxplot(aes(fill=supp)) +
  facet_grid(~ dose)
```

Thirdly, use t.test() to check the confidence interval.
```{r confidence interval}
t.test(len~supp,data = ToothGrowth)
t.test(len~dose,data = subset(ToothGrowth,dose == 0.5|dose == 1))
t.test(len~dose,data = subset(ToothGrowth,dose == 1|dose == 2))
```